---
title: "DATA607 Project 4"
author: "ODONNELL"
date: "April 9, 2019"
output: html_document
---

load the needed packages
```{r}
library(tm)
library(stringr)
library(ggplot2)
library(caret)
library(rpart)
```

importing the emails into a corpus
```{r}
ham_emails<-Corpus(DirSource(directory="easy_ham"))
spam_emails<-Corpus(DirSource(directory="spam"))
attributes(ham_emails)

#summary(ham_emails)
```

As I am having difficulty with the corpus, let's turn
the corpus into a dataframe..
And, we will label each email spam or ham with a flag
```{r}
ham_emails_df <- data.frame(text = get("content", ham_emails))
ham_emails_df$spam <- 'N'


spam_emails_df <- data.frame(text = get("content", spam_emails))
spam_emails_df$spam <- 'Y'
```

Now, let's pick out some important pieces of data in each ham email
```{r}
ham_emails_df$sender <- str_extract(ham_emails_df$text, "From[[:punct:]]{1}.{1,200}")
ham_emails_df$recipient <- str_extract(ham_emails_df$text, "To[[:punct:]]{1}.{1,200}")
ham_emails_df$subject <- str_extract(ham_emails_df$text, "Subject[[:punct:]]{1}.{1,200}")
ham_emails_df$date <- str_extract(ham_emails_df$text, "Date[[:punct:]]{1}.{1,200}")
```

And, let's do the same for each spam email
```{r}
spam_emails_df$sender <- str_extract(spam_emails_df$text, "From[[:punct:]]{1}.{1,200}")
spam_emails_df$recipient <- str_extract(spam_emails_df$text, "To[[:punct:]]{1}.{1,200}")
spam_emails_df$subject <- str_extract(spam_emails_df$text, "Subject[[:punct:]]{1}.{1,200}")
spam_emails_df$date <- str_extract(spam_emails_df$text, "Date[[:punct:]]{1}.{1,200}")
```

Now let's combine the dataframes!
```{r}
email_df <- rbind(ham_emails_df, spam_emails_df)
email_df <- subset(email_df, select = -c(text))
email_df <- email_df[complete.cases(email_df), ]
```

Sort our data into training and testing datasets
```{r}
intrain <- createDataPartition(y = email_df$spam, p= 0.7, list = FALSE)
training <- email_df[intrain,]
testing <- email_df[-intrain,]

dim(training)
dim(testing)
```
Fit a Decision tree with rpart
```{r}
fit<- rpart(spam ~ subject + sender + recipient,
   method="class", data=training)

printcp(fit)
```
predict the amount of spam vs ham!
```{r}
table(predict(fit, type = "class"))
```